Numerical Stability of Detonations in White Dwarf Simulations

### 2019-02-06 papers/ignition/paper.tex
Clean up conclusion

Our example detonation problem demonstrates, at least for this class of
hydrodynamical burning problem, a grid resolution requirement much more stringent
than 1 km. This does not represent all such \added{1D} burning problems: for example, we
have tested similar setups with only carbon and oxygen for which a resolution
in the tens of kilometers is sufficient. \added{However, this should not be construed
as implying that this convergence requirement does not apply to pure C/O WDs.}
\replaced{However}{First}, the fact that it is even possible for
\replaced{this type of burning}{burning in white dwarf material} to require a
resolution better than 100 m should cast significant uncertainty on the results
of simulations featuring detonations that do not meet this resolution
\added{(regardless of the specific conditions). Or, at least, should suggest
that stronger demonstrations of convergence are required. Second, in our real
multi-dimensional simulations of C/O WD collisions, we see the same effect,
where the simulation is not converged even for resolutions up to 0.25 km. It
simply happens to be the case that for the 1D analogue of this problem using pure
C/O the same effect is not seen, which is not particularly surprising since the 1D
setup and the 2D setup are very different and the former lacks any multidimensional
hydrodynamic effects. So we found a related problem that shows a similar
effect in 1D to test convergence at higher resolutions.}

>>>>

Our example detonation problem demonstrates, at least for this class of
hydrodynamical burning problem, a grid resolution requirement much more stringent
than 1 km. \replaced{This does not represent all such burning problems: for example, we
have tested similar setups with only carbon and oxygen for which a resolution
in the tens of kilometers is sufficient.}{This test does not, of course, represent
all possible WD burning conditions.}
However, the fact that it is even possible for
\replaced{this type of burning}{burning in white dwarf material} to require a
resolution better than 100 m should cast significant uncertainty on the results
of simulations featuring detonations that do not meet this resolution,
\added{regardless of the specific conditions). Or, at least, it should suggest
that stronger demonstrations of convergence are required (especially bearing in mind
our observation that the numerical instability can result in simulations that
appear qualitatively converged when the resolution is increased by a factor of
one or two orders of magnitude but not three orders of magnitude.}
